### 2020-10-12 input/background.tex
small changes

\begin{definition}[Dynamic optimal partitioning]
  \TODO{add and del operations.}
\end{definition}

\TODO{Figure.} \TODO{Also easy to solve when all
  processes receive all messages}. One could solve this issue by
removing partitions that were not advertised for a defined
time~\REF. However, relying on physical timeout could lead to either
premature removals of partitions when they are still operating; or
slow convergence where processes believe they belong to a partition
that was removed.

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:delA}Both Process $a$ and
      Process $c$ initiate then remove a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figdelA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:delB}Process $b$ and Process $d$ receive and deliver
      messages based on their weights. $a$'s partition propagates to all processes.]
             {\input{input/figdelB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:delC}Process $c$'s partition reach $b$ and $d$.
      Its removal shortly follows. Process $b$ does not have any control
      information about partitions any more.]{\input{input/figdelC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:delD}Processes discard remaining messages.
      Process $b$ does not deliver $\delta_a$, for it already removed $a$ when
      Partition $c$ dominated it. Processes $c$ and $d$ remain in an incorrect
      partition.]{\input{input/figdelD.tex}}
  \end{center}
  \caption{\label{algo:add}Removing partition may lead to inconsistent partitions.}
\end{figure*}

\TODO{Problem statement.}

>>>>

\begin{definition}[Dynamic optimal partitioning]
  A dynamic optimal partitioning is an optimal partitioning where the
  set of sources $S$ does not monotonically increase. Process $i$
  joins the set of sources by adding its partition $\alpha_i^{0}$ and
  leaves the set of sources by removing its partition $\delta_i$.
\end{definition}

\TODO{Figure~\ref{fig:del} shows that.}

One could solve this issue by using a conflict-free replicated data
type for set data structures, then deliver and broadcast all
operations to all processes~\REF. However, this would be costly in
terms of generated traffic with some processes delivering and
broadcasting unrelated to their partitions \TODO{(include locality)}.
One could also solve this issue by removing partitions that were not
advertised for a defined time~\REF. However, relying on physical
timeout could lead to either premature removals of partitions when
they are still operating; or slow convergence where processes believe
they belong to a partition that was removed.

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:delA}Both Process $a$ and
      Process $c$ initiate then remove a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figdelA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:delB}Process $b$ and Process $d$ receive and deliver
      messages based on their weights. $a$'s partition propagates to all processes.]
             {\input{input/figdelB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:delC}Process $c$'s partition reach $b$ and $d$.
      Its removal shortly follows. Process $b$ does not have any control
      information about partitions any more.]{\input{input/figdelC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:delD}Processes discard remaining messages.
      Process $b$ does not deliver $\delta_a$, for it already removed $a$ when
      Partition $c$ dominated it. Processes $c$ and $d$ remain in an incorrect
      partition.]{\input{input/figdelD.tex}}
  \end{center}
  \caption{\label{fig:del}Partition removals cannot rely only on
    current partition, for it may lead to inconsistent partitioning.}
\end{figure*}

\begin{problem}[Consistent partitioning]
  \TODO{How to enable \emph{consistent} dynamic optimal partitioning
    with contained broadcast?}
\end{problem}
